---
title: "Worksheet 3"
output: html_notebook
---
#Prelim: Make testing dataframes
```{r}
#Making test df1 (present)

A <-  round(runif(100,1,6)) 

B <-  round(runif(100,1,6)) 

C <-  round(runif(100,1,6)) 

D <-  round(runif(100,1,6)) 

E <-  round(runif(100,1,6))  

F <-  round(runif(100,1,6)) 

df1 <- cbind(A, B, C, D, E, F)
df1 <- as.data.frame(df1)
rm(A, B, C, D, E, F)

#Making vector of suspect positions for df1
pos1 <- c(1, 2, 3, 4, 5, 6)

#Making test df2 (absent)

A <-  round(runif(100,1,6)) #Present 

B <-  round(runif(100,1,6)) #Absent 

C <-  round(runif(100,1,6)) #Present 

D <-  round(runif(100,1,6)) #Absent

E <-  round(runif(100,1,6)) #Present 

F <-  round(runif(100,1,6)) #Absent

df2 <- cbind(A, B, C, D, E, F)
df2 <- as.data.frame(df2)
rm(A, B, C, D, E, F)

#Making vector of suspect positions for df2
pos2 <- c(1, 2, 3, 4, 5, 6)

```

#Step 1: Get parameters for all lineups

```{r}
diag_param <- function(df1, df2, pos1, pos2){
    diagdf1 <- as.data.frame(matrix(ncol = 2, 
                                    nrow = length(df1)))
    
    for (i in 1:ncol(df1)){
        diagdf1[i, 1]= sum(df1[i] == pos1[i])
        diagdf1[i,2] = sum(df1[i] != pos1[i])
        
        diagdf2 <- as.data.frame(matrix(ncol = 2, 
                                        nrow = length(df2)))
    }
    
    for (i in 1:ncol(df2)){
        diagdf2[i,1]= sum(df2[i] == pos2[i])
        diagdf2[i,2] = sum(df2[i] != pos2[i]) 
        
        diagdf <- cbind(diagdf1, diagdf2)
        names(diagdf) <- c("n11", "n21", "n12", "n22")
        
    }
    return(diagdf)
}

linedf <- diag_param(df1, df2, pos1, pos2)

```

#Step 2: Get ln(d) for each pair of lineups
```{r}
ln_diag_ratio <- function(df){
    d<- (df$n11+0.5/((df$n11+df$n21)+0.5))/
        (df$n12+0.5/((df$n12+df$n22)+0.5))
    lnd <- log(d)
    ratio <- as.data.frame(cbind(d, lnd))
    
    return(ratio)
}

ratio <- ln_diag_ratio(linedf)
```

#Step 3: Get var(lnd) for each diagnosticity ratio

```{r}
var_lnd <- function(df){
    var <- (df$n21/(df$n11+(df$n11+df$n21)))+(df$n22/(df$n12+(df$n12+df$n22)))
    var <- as.data.frame(var)
    return(var)
}

var <- var_lnd(linedf)
```

#Step 4: Get wi for each diagnosticity ratio

```{r}
d_weights <- function(df){
    numerator <- df$n11*df$n12*(df$n11+df$n21)*(df$n12+df$n22)
    denominator <- df$n11*df$n22*(df$n11+df$n21)+
        df$n12*df$n21*(df$n12+df$n22)
    wi <- numerator/denominator
    wi <- as.data.frame(wi)
    return(wi)
    
}

wi <- d_weights(linedf)

```

#Step 5: Combine vectors for lnd, var(lnd) and wi into one df
```{r}
param2 <- cbind(ratio, var, wi)

```
#Step 6: Get pooled estimator for set of n diagnosticity ratios

```{r}
d_bar <- function(df){
    numerator <- sum(df$wi*df$lnd)
    denominator <- sum(df$wi)
    d_bar <- exp(numerator/denominator)
    return(d_bar)
}

d_bar <- d_bar(param2)
```

#Step 7: Get chi squared value
```{r}
chi_diag <- function(df, d_bar){
    q <- sum(((df$lnd-log(d_bar))^2)/(df$var))
    return(q)
}

q <- chi_diag(param2, d_bar)
    
```

#Step 8: Get significance value, given chi, df and desired alpha
```{r}
pchisq(q, 5, lower.tail = T)

```

##Still needs: Functions for bootstrapped estimates

##Will need to get different CIs for each? Or is it only For the p value....