---
title: "R Notebook"
output: html_notebook
---
#Test code
```{r}
linedata <- lineup_data_raw$lineup_1_data
linetab <- table(linedata)

pos <- c(1, 2, 3, 4, 5, 6, 7, 8)

library(pacman)
p_load(tidyverse, magrittr, purrr, boot, slipper)


```

```{r}
#Need this fx
lineup_prop_pos_vec <- function(linevec, susp_pos){
    sum(linevec == susp_pos)/length(linevec)
}
```


```{r}
#Function for computing proportion for each lineup member
#What about cases in which a member wasn't chosen at all? Data should reflect this - how?
#What about cases in which mock witness chose no one?
allprop <- function(linevec, susp_pos){
    propvec <- as.data.frame(matrix(ncol= 1,
                                    nrow = length(susp_pos)))
    for (i in 1:length(susp_pos)){
       propvec[i,]=lineup_prop_pos_vec(linevec, susp_pos[i])
    }
    return(propvec)
}

allprop(linedata, pos)
```


```{r}
#Attempting to bootstrap fx above
allprop_boot <- function(linevec, d, susp_pos){
    propvec <- as.data.frame(matrix(ncol= 1,
                                    nrow = length(susp_pos)))
    for (i in 1:length(susp_pos)){
       propvec[i,]=lineup_prop_pos_vec(linevec, susp_pos[i])
    }
    return(propvec)
}

bootfx <- boot(linedata, allprop_boot, susp_pos = pos, R=100)

```

Alternatively, change format of function

is there a way to loop through susp pos without using a loop?
Could add argument like: for each unique value in df
```{r}
lineup_prop_pos_a<- function(linevec){
    pos <- sort(unique(linevec))
    for (i in 1:length(pos)){
    df[i,]= sum(linevec == pos[i])/length(linevec)
    }
    return(df)
}

lineup_prop_pos_a(linedata)

lineup_prop_pos_a<- function(linevec, d){
    pos <- sort(unique(linevec))
    d <- linevec
    for (i in 1:length(pos)){
    df[i,]= sum(linevec == pos[i])/length(linevec)
    }
    return(df)
}



```
 you will be running the bootstrap 1000 x k times


lineup_boot <- function(linevec, d=d,  susp_pos){
    sum(linevec[d] == susp_pos)/length(linevec)
}

then 

boot(linevec, lineup_boot, 1, R=1000)
boot(linevec, lineup_boot, 2, R=1000)
boot(linevec, lineup_boot, 3, R=1000)
etc, to end of pos




```{r}
list1 <- list(linedata, pos)
```


```{r}
#Same fx above, but takes a list
allprop_list <- function(list){
    propvec <- as.data.frame(matrix(ncol= 1,
                                    nrow = length(list[[2]])))
    for (i in 1:length(list[[2]])){
       propvec[i,]= sum(list[[1]] == list[[2]][i])/length(list[[1]])
}
    return(propvec)
}

all_props <- allprop_list(list1)
```

```{r}
allprop_list_boot <- function(list, d){
    d <- list[[1]]
 return(allprop_list(list[d]))
}

bootfx3 <- boot(list1, allprop_list_boot, R=100)


```


```{r}
#Fx for finding bootstrapped ci of proportion for 1 lineup member
lineup_prop_pos_vec_boot <- function(linevec, d=d,  susp_pos){
    sum(linevec[d] == susp_pos)/length(linevec)
}

bootfx2 <- boot(linedata, lineup_prop_pos_vec_boot, susp_pos =3, R=1000)

bootfx2
boot.ci(bootfx2, type = "all")
```

```{r}
esize_m_boot <- function (linevec, d, printarg=FALSE){
    linetable <- table(linevec[d])
    k <- length(linetable)
    ea <- sum(linetable)/k
    x <- sum(abs(linetable-ea)/(2*ea))
    esize_ma = k-x
    ka <- sum(linetable!=0)
    linetable_a <- linetable[linetable!=0]
    ea <- (sum(linetable))/ka
    xa <- sum(abs(linetable_a-ea)/(2*ea))
    esize_ma_a = ka-xa
    if (printarg) {
        cat("Effective size (Malpass, 1981) = ", esize_ma_a,"\n")
        cat("Effective size (Malpass, 1981,","\n", 
            "            adj Tredoux, 1998) = ", esize_ma, "\n")
    }
    esize_ma
}

boot_esize <- boot(linedata, esize_m_vec, R=1000)
ci <- boot.ci(boot_esize, type = "all")
boot_esize
ci
```
So now we can say that if lineup is unbiased, probability that any member/suspect is chosen is = 1/5.962406

```{r}
1/boot_esize$t0
```
So CI for chance guessing = 1/5.650 and 1/6.594

```{r}
1/ci$normal[2:3]

```
CI for chance guessing = 0.18 and 0.15

What we're trying to figure out - were any lineup members selected at a rate greater or smaller than this?

```{r}
all_props
```
A) Do we compare bootstrapped prop to CI above?
or do we compare ci of bootstrapped prop to CI above?

0.22+
